\mytitle

### 2012-03-12 papers/SAS2012/implicitization.tex
rqs Nicolas

An additional claim of the methods that distinguish paths inside the loop body \cite{DBLP:conf/pldi/GulwaniZ10,Monniaux_Gonnord_SAS11} is that they tend to generate better invariants than methods that do not, by behaving better with respect to the \emph{widening operators} \cite{CousotCousot_JLC92}
used for enforcing convergence when searching for loop invariants by Kleene iterations. A related technique, \emph{guided static analysis} \cite{DBLP:conf/sas/GopanR07}, computes successive loop invariants for increasing subsets of the transitions taken into account, until all transitions are considered; again, the claim is that this approach avoids some gross over-approximation introduced by widenings.

@@

\emph{Widening-accelerated Kleene iterations} proceed by replacing $\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p)$ by $\abstr{x}_{p'} \widening (\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p))$ where $\widening$ is a \emph{widening operator}: for all $\abstr{x},\abstr{y}$, $\gamma(\abstr{y}) \subseteq \gamma(\abstr{x} \widening \abstr{y})$, and there exists no sequence $\abstr{u}_1,\abstr{u}_2,\dots$ of the form $\abstr{u}_{n+1} = \abstr{u}_n \widening \abstr{v}_n$ where $\abstr{v}_n$ is another sequence.
Such iterations necessarily lead to a stationary limit $(\abstr{x}_p)_{p \in P}$, which defines an inductive invariant $(\gamma(\abstr{x}_p))_{p \in P}$. Note that this invariant is not, in general, the least one expressible in the abstract domain, and may depend on the iteration ordering (the successive choices~$p,p'$).

>>>>

An additional claim in favor of the methods that distinguish paths inside the loop body \cite{DBLP:conf/pldi/GulwaniZ10,Monniaux_Gonnord_SAS11} is that they tend to generate better invariants than methods that do not, by behaving better with respect to the \emph{widening operators} \cite{CousotCousot_JLC92}
used for enforcing convergence when searching for loop invariants by Kleene iterations. A related technique, \emph{guided static analysis} \cite{DBLP:conf/sas/GopanR07}, computes successive loop invariants for increasing subsets of the transitions taken into account, until all transitions are considered; again, the claim is that this approach avoids some gross over-approximation introduced by widenings.

@@

\emph{Widening-accelerated Kleene iterations} proceed by replacing $\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p)$ by $\abstr{x}_{p'} \widening (\abstr{x}_{p'} \sqcup \abstr{\tau}_{p,p'} (\abstr{x}_p))$ where $\widening$ is a \emph{widening operator}: for all $\abstr{x},\abstr{y}$, $\gamma(\abstr{y}) \subseteq \gamma(\abstr{x} \widening \abstr{y})$, and any sequence $\abstr{u}_1,\abstr{u}_2,\dots$ of the form $\abstr{u}_{n+1} = \abstr{u}_n \widening \abstr{v}_n$, where $\abstr{v}_n$ is another sequence, become stationary.
The stationary limit $(\abstr{x}_p)_{p \in P}$, defines an inductive invariant $(\gamma(\abstr{x}_p))_{p \in P}$. Note that this invariant is not, in general, the least one expressible in the abstract domain, and may depend on the iteration ordering (the successive choices~$p,p'$).
